
%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Sanjay Prabhakar} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 571-356-6100 ~ \href{mailto:prabhakar.sa@northeastern.edu}{\raisebox{-0.2\height}\faEnvelope\  \underline{prabhakar.sa@northeastern.edu}} ~ 
    \href{https://linkedin.com/in/sanjay-prabhakar-northeastern}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/sanjay-prabhakar-northeastern}}  ~
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Northeastern University  \hspace{230pt} GPA-3.87}{Sept. 2022 -- Dec. 2024}
      {Master of Science in Artificial Intelligence (Khoury College of Computer Sciences)}{Boston, Massachusetts}
      {\newline \textbf{Related Courses:} Large Language Models, Robotic Science Systems, Foundations of Artificial Intelligence, Computer Vision, Machine Learning}
      
    \resumeSubheading
      {BMS Institute of Technology\hspace{210pt} GPA-3.3}{Aug. 2018 -- Jun. 2022}
      {Bachelor of Engineering in Computer Science}{Bangalore, India}
      {\newline \textbf{Related Courses:} Artificial Intelligence \& ML, Advanced Engineering Mathematics, Data Structures, Algorithm Analysis, Computer Graphics}
      
  \resumeSubHeadingListEnd
%-----------PROGRAMMING SKILLS-----------
\section{Technical Knowledge}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, C++, C, SQL} \\
     \textbf{Databases}{: MySQL} \\
     \textbf{Skills}{: Computer Vision, Stereo Vision, CNN, Machine Learning, Deep Learning} \\
     \textbf{Libraries}{: PyTorch, Keras, TensorFlow, Scikit-Learn, DepthAI} \\
     \textbf{Certifications}{: OpenCV for Python, Modern Computer Vision (PyTorch, TensorFlow, Keras), Nvidia Deep Learning (DLI)
    
    }}}
 \end{itemize}
 \vspace{-20pt}



%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
\vspace{5pt}

   \resumeSubheading
      {Agot AI}{August 2023 -- December 2023}
      {Machine Learning Intern}{Pittsburgh, Pennsylvania}
      \resumeItemListStart
        \resumeItem{Led the development and successful launch of an innovative food waste management product, utilizing a novel ML algorithm for data forecasting and vision data, achieving a 50\% reduction in wastage. This role involved overseeing the entire product lifecycle from concept to deployment on the edge.}
        \resumeItem{Developed an action recognition pipeline using Generative and Discriminative Learning Models for restaurant behavioral analysis.}
    \resumeItemListEnd

 \resumeSubheading
      {Agot AI}{May 2023 -- August 2023}
      {Computer Vision Intern}{Pittsburgh, Pennsylvania}
      \resumeItemListStart
        \resumeItem{Optimized segmentation models with Nvidia TAO \& Deepstream, improving IOU by 20\% and deployed on Nvidia Xavier \& Orin.}
        \resumeItem{Integrated visual language models such as \textbf{GPT-4V} and \textbf{LLaVa} into computer vision pipelines, enabling multimodal understanding and enhancing complex scene interpretation accuracy by 30\%.}
        \resumeItem{Trained transformer-UNet based segmentation and detection models on AWS Sagemaker,PyTorch and deployed on Kubernetes cluster using Argo CD and Docker for automated deployment.}

    \resumeItemListEnd

 \resumeSubheading
      {Green Robot Machinery (Grobomac)}{June 2021 -- December 2021}
      {Computer Vision Intern}{Bangalore, Karnataka}
      \resumeItemListStart
        \resumeItem{Developed \& deployed real-time depth estimation and object tracking for autonomous cotton-harvesting robots using Python, C++, OpenVino, and DepthAI.}
        \resumeItem{Evaluated edge devices like Nvidia Jetson series \& OAK-D for cost and performance.}
        \resumeItem{Boosted FPS by 40\% with a neural model, reducing compute resources by 50\%.}
     \resumeItemListEnd
  
  \resumeSubHeadingListEnd
\vspace{-10pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{5pt}
    \resumeSubHeadingListStart
        
          
    \resumeProjectHeading
          {\textbf{Alzheimer’s Detection Using Vision Transformers} $|$ \emph{Python, PyTorch, ViT}}{March 2024}
          \resumeItemListStart
            \resumeItem{\textbf{Pretrained Model Integration:} Utilized the pretrained ViT-B16 weights for deep learning.}
            \resumeItem{\textbf{Diagnostic Classification:} Developed capabilities for the transformer to classify the level of dementia from MRI scans.}
             \vspace{-12pt}
            \resumeItem{\textbf{Data Handling:} Trained the Vision Transformer (ViT) on MRI scans from patients with varying levels of dementia.}
       \resumeItemListEnd 
           \vspace{-12pt}
       \resumeProjectHeading
        {\textbf{Latent Diffusion Based Image Enhancer} $|$ \emph{Python, OpenCV, PyTorch}}{June 2023}
          \resumeItemListStart
            \resumeItem{\textbf{Advanced Enhancement:} Integrated a latent image diffusion model for superior image quality.}
            \resumeItem{\textbf{Practical Application:} Designed for optimizing, refining, and latent upscaling images captured on smartphones.}
       \resumeItemListEnd 
          

      \vspace{-15pt}

    \resumeSubHeadingListEnd
\end{document}

